\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-02-22 papers/itsc_2012/draft2.tex
small typos fixed

All traversables (edges and the straight line-approximation of turns) maintain
an ordered \emph{queue} of occupying agents. Agents stepping forward in time
happens atomically, so collision checking occurs after all agents have moved for
some tick. This is done because otherwise false positives could occur when an
agent steps before the agent in front of it, and ordering agents for updates is
difficult near the crossings between edges. \commentd{Do I need to explain why
it is difficult, or should I just stop after ``in front of it''?} A collision is
defined as the reversal of order of agents before and after a step.

@@

When a collision occurs, the simulator throws warnings or halts, since this
indicates a bug in some policy. A future alternative could be to mark the region
as impassable and re-route other traffic away from the accident.

@@

Each agent has a ``behavior'' governing it. When the agent travels past the end
of an edge during its step, the behavior picks the turn to pursue. Each tick,
the behavior can make the agent react by performing one of two actions:
disappearing from the map (only when the agent is at rest and is done with its
route) or setting an acceleration for the next step. Were lane changing or
merging modeled, that would be another possible action.

@@

The default behavior maximizes accelerations while obeying speed limits,
avoiding collisions, and obeying intersections. By consdering the highest speed
achievable at the end of the next tick and the subsequent stopping distance at
this speed, the behavior can scan sufficiently far ahead along several
traversables to locate agents to avoid and intersections to query. The analysis
can short-circuit at the first nearby agent and intersection requiring a stop,
since it would be illegal to pass either.

@@

Picking accelerations that optimize some objective functions is a separate task
from picking a path to travel. Behaviors consult a route strategy to pick turns.
Currently two simple implementations are available. One statically plans a route
to some goal using standard A* search; the other performs a drunken walk, lazily
planning random choices at each intersection as the lookahead engine needs to
know. Future experiments in dynamic replanning or hierarchial planning can be
performed without modifying any code other than a creating new route
implementation. Route policies could also interact with a singleton overseer to
have some sort of global insight.

>>>>

All traversables (edges and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. Agents stepping forward in time happens
atomically, so collision checking occurs after all agents have moved for some
tick. This is done because otherwise false positives could occur when an agent
steps before the agent in front of it, and ordering agents for updates is
difficult near the crossings between edges. \commentd{Do I need to explain why
it is difficult, or should I just stop after ``in front of it''?} A collision is
defined as the reversal of order of agents before and after a step.

@@

When a collision occurs, the simulator throws warnings and halts, since this
indicates a bug in some policy. A future alternative could be to mark the region
as impassable and re-route other traffic away from the accident.

@@

Each agent has a \emph{behavior} governing it. When the agent travels past the end
of an edge during its step, the behavior picks the turn to pursue. Each tick,
the behavior can make the agent react by performing one of two actions:
disappearing from the map (only when the agent is at rest and is done with its
route) or setting an acceleration for the next step. Were lane changing or
merging modeled, that would be another possible action.

@@

The default behavior maximizes acceleration while obeying speed limits,
avoiding collisions, and obeying intersections. By considering the highest speed
achievable at the end of the next tick and the subsequent stopping distance at
this speed, the behavior can scan sufficiently far ahead along several
traversables to locate agents to avoid and intersections to query. The analysis
can short-circuit at the first nearby agent and intersection requiring a stop,
since it would be illegal to pass either.

@@

Picking accelerations that optimize some objective functions is a separate task
from picking a path to travel. Behaviors consult a route strategy to pick turns.
Currently two simple implementations are available. One statically plans a route
to some goal using standard A* search (TODO cite); the other performs a drunken
walk, lazily planning random choices at each intersection as the lookahead
engine needs to know. Future experiments in dynamic replanning or hierarchial
planning can be performed without modifying any code other than a creating new
route implementation. Route policies could also interact with a singleton
overseer to have some sort of global insight.
